Goals and Tasks

### 2020-05-22 README.Rmd
fix componentwise boosting for beta

@@

```{r}
library(asp20boost)
model <- LocationScaleRegressionBoost$new(y ~ x, ~ x)
gradient_boost(model, 
              stepsize = 0.001, maxit = 1000,
              abstol = 0.001,
              verbose = FALSE)
plot(x, y)
lines(x,model$fitted_location)
#Todo do create similar graphic
curve(x + 1.96 * exp(x*model$gamma), -0.1, 1.1, add = TRUE)
curve(x - 1.96 * exp(x*model$gamma), -0.1, 1.1, add = TRUE)

>>>>

model$gamma
```

```{r fig.width = 11, echo=FALSE}
library(asp20boost)
model <- LocationScaleRegressionBoost$new(y ~ x, ~ x)
gradient_boost(model, 
              stepsize = 0.001, maxit = 10000,
              abstol = 0.001,
              verbose = FALSE)

plot(x, y)
lines(x,model$fitted_location)
#For a 95% confidence interval, the value c = 1.96 is agood approximation
curve(x + 1.96 * exp(model$gamma[1]+model$gamma[2]*x), -0.1, 1.1, add = TRUE)
curve(x - 1.96 * exp(model$gamma[1]+model$gamma[2]*x), -0.1, 1.1, add = TRUE)

@@
